lab_notebook

### 2018-11-15 lab_notebook.Rmd
creating turf/itq data set almost done

#Loading packages
```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})

@@

#Simplified Projection Data
ITQ_projection_simple <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")

#create RDS from datafram
#saveRDS(ITQ_projection_simple, "projection_updated.rds")

@@

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "Year", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

#rearrange columns
all_turf_2 <- all_turf_1[, c(1,3,5,2,6,7,8,9,4)]

#turning NAs from no ITQ data to FALSE

all_turf_2 %>% replace(is.na(.), FALSE)

>>>>

#Loading packages
```{r}

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})

@@

#simplified projection data
ITQ_projection_simple <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")

#create RDS from dataframe
#saveRDS(ITQ_projection_simple, "projection_updated.rds")

#upside updated
upside_2018_updated <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")

#create RDS from dataframe
#saveRDS(upside_2018_updated, "upside_2018_updated")

@@

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

#rearrange columns
all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]

#turning NAs from no ITQ data to FALSE
#all_turf_2$itq_now[all_turf_2$itq_now == 0] <- NA

#all_turf_2 %>% replace(is.na(.), FALSE)

#doublecheckworked <- all_turf_2 %>%
#  filter( itq_now == "1" & turf == "TRUE")
